### 2024-12-25 download-football-data.qmd
20241225 - fix error

```{r}
nfl_actualFantasyPoints_player_seasonal <- nfl_actualFantasyPoints_player_seasonal_raw %>% 
  rename(fantasyPoints = raw_points) %>% 
  select(player_id, season, everything()) %>% 
  arrange(player_display_name, player_id, season)

>>>>

```{r}
nfl_actualFantasyPoints_player_seasonal <- nfl_actualFantasyPoints_player_seasonal_raw %>% 
  rename(
    fantasyPoints = raw_points,
    team = recent_team) %>% 
  select(player_id, season, everything()) %>% 
  arrange(player_display_name, player_id, season)
